On the computational complexity of detecting possibilistic locality

### 2017-06-15 paper.tex
Abstract is more concrete: the phrase "table of possibilities" now explained.

\begin{document}
\title{On the computational complexity of detecting possibilistic locality}
\author{Andrew W. Simmons}\affiliation{Department of Physics, Imperial College London, SW7 2AZ.}
\begin{abstract}
The proofs of quantum nonlocality due to GHZ and Hardy are quantitatively different from that of Bell insofar as they rely only on a consideration of whether events are possible or impossible, rather than relying on specific experimental probabilities. Here, we consider the computational task of determining whether or not a given table of possibilities constitutes a departure from possibilistic local realism. By considering the case in which one party has access to measurements with two outcomes and the other three, it is possible to see at exactly which point this task becomes computationally difficult.
\end{abstract}
\maketitle

@@

I would like to thank Terry Rudolph for multiple helpful discussions, and acknowledge support from Cambridge Quantum Computing Limited and from EPSRC \emph{via} the Centre for Doctoral Training in Controlled Quantum Dynamics..

>>>>

\begin{document}
\title{On the computational complexity of detecting possibilistic locality}
\author{Andrew W. Simmons}\affiliation{Department of Physics, Imperial College London, SW7 2AZ.}
\begin{abstract}
The proofs of quantum nonlocality due to Greenberger, Horne and Zeilinger, and by Hardy are qualitatively different from that of Bell insofar as they rely only on a consideration of whether events are possible or impossible, rather than relying on specific experimental probabilities. We consider the scenario of a bipartite nonlocality experiment, in which two separated experimenters each have access to some measurements they can perform on a system; in a physical theory, some outcomes of this experiment will be considered possible, others impossible, and an assigment of the values``possible" and ``impossible" to these different outcomes forms a table of possibilities. Here, we consider the computational task of determining whether or not a given table of possibilities constitutes a departure from possibilistic local realism. By considering the case in which one party has access to measurements with two outcomes and the other three, it is possible to see at exactly which point this task becomes computationally difficult.
\end{abstract}
\maketitle

@@

I would like to thank Terry Rudolph for multiple helpful discussions, and acknowledge support from Cambridge Quantum Computing Limited and from EPSRC \emph{via} the Centre for Doctoral Training in Controlled Quantum Dynamics.
